\documentclass[letterpaper]{article}
\usepackage[utf8]{inputenc}

% Fonts
\usepackage{fontspec}
\setromanfont[Ligatures = TeX]{Libre Baskerville}

% Headings
\newcommand{\subsectiondate}[2]{\subsection*{#1\hfill#2}}

% Lists
\usepackage{enumitem}
\setlist{itemsep=.01em}

% Links
\usepackage{hyperref}

% Spacing
\setlength{\parindent}{0pt}
\usepackage[compact]{titlesec}

% Disable Page Numbers
\pagenumbering{gobble}

% Margins
\usepackage[top=.5in, bottom=.5in, left=1in, right=1in]{geometry}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
    {\LARGE Michael Younkin}

    \href{mailto:younkin.michael@gmail.com}{younkin.michael@gmail.com} |
    \href{https://www.linkedin.com/in/michaelyounkin}{www.linkedin.com/in/michaelyounkin} |
    410-707-0956
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Education}

\subsectiondate{University of Maryland, College Park}{2012--2016}

\begin{itemize}
    \item B.S. Computer Science
    \item Cumulative GPA\@: 3.4
    \item Technology Entrepreneurship Minor
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Internships
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Internships}

\subsectiondate{Amazon.com}{2015}

\begin{itemize}
    \item Researched methods to improve machine learning model accuracy.
    \item Designed and implemented model improvement algorithm running on AWS.
\end{itemize}

\subsectiondate{Bloomberg L.P.}{2014}

\begin{itemize}
    \item Designed and implemented internal API for OpenTSDB.
    \item Implemented data visualization and analysis toolkit for services metrics data.
\end{itemize}

\subsectiondate{NASA Jet Propulsion Laboratory}{2013}

\begin{itemize}
    \item Designed and implemented RESTful API for Mars rover backup data.
    \item Designed and implemented archived research data visualization system.
\end{itemize}

\subsectiondate{Applied Media Analysis, Inc.}{2012--2013}

\begin{itemize}
    \item Implemented Arabic text processing system to fix corrupted PDF files.
    \item Refactored legacy Perl scripts, improving efficiency and reducing maintenance costs.
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Other Experience}

\subsectiondate{TA for CMSC330}{2015--2016}

\begin{itemize}
    \item Taught Ruby, OCaml, Prolog, Regexps, NFAs, DFAs, CFGs, LL(1) parsers
    \item Worked with professors to manage curriculum and other TAs
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Skills}

\subsection*{Best Languages (subject to fluctuation)}
Python, Rust, Java, JavaScript, C, Lambda Calculus

\subsection*{Most Knowledgable In}
Low Level Computer Systems, Full Stack Web Development

\subsection*{Tools of Choice}
git, (neo)vim, tmux, fish shell

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Footer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Personal Projects}
I work on my personal projects almost every day (in my free time, of course).
You can checkout my projects at \href{https://github.com/michael-younkin}{https://github.com/michael-younkin}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% End Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
